\section{Test Reports}
\subsection{TR001}
\tr{T008}{AC008}{1}{BL012}{VPQ-21}
   {\shortstack[l]{GIVEN that we have an estimated mass AND that we have four motors.\\ 
                   WHEN we provide 50 percent thrust. THEN the quadrotor shall hover.}}
\subsubsection{\textsc{\medium Test Procedure}}

\paragraph{Test Method:}\mbox{}\\
Static Testing through analysis and calculation.

\paragraph{Test Information:}\mbox{}\\
\begin{itemize}
\item  The propeller thrust given from the supplier, is at optimal conditions so it is a theoretical value. The actual thrust differs from propeller to propeller. A variable pitch propeller is symmetric, and therefore i will have less thrust than fixed pitch propellers. The thrust given from supplier is given at FPQ. This must be considered when estimating or calculating the actual thrust from propellers.
\item Max trust in grams must be at least twice the mass of the quadrotor
\item If the quadrotor has liftoff at 50 percent trust or less, the test is fulfilled.
\item The optimal thrust of each propeller $tr_p$ is $x_1$ grams
\item This gives a total thrust of
    \begin{equation}
    \begin{split}
        tr_{tot} = x_1\cdot4 = x_2
    \end{split}
    \end{equation}
\item The total mass of the quadrotor in  grams shall be:
    \begin{equation}
    \begin{split}
        x_2 \geq 2\cdot m_{quadcopter} 
    \end{split}
    \end{equation}
\end{itemize}
\paragraph{Test Steps:}\mbox{}\\
\paragraph{Test Equipment:}\mbox{}\\
No special equipment needed.
\subsubsection{\textsc{\medium Analysis:}}
\subsubsection{\textsc{\medium Test Result(s):}}

\newpage

