% Sprint 1
\subsection*{T001}
\testcard{T001}{AC001}{1}{BL013}{VPQ-29}
         {\shortstack[l]{GIVEN that we have arduino car. WHEN we run arduino script. \\                                 THEN the car will move as descripted in the code.}}
         {\shortstack[l]{Inspection, observe that the arduino car moves as descripted.\\}}
         {\shortstack[l]{}}
         {\shortstack[l]{}}
\subsection*{T002}
\testcard{T002}{AC002}{1}{BL013}{VPQ-29}
         {\shortstack[l]{GIVEN that we have arduino car. WHEN we run python script. \\ 
                         THEN the car will receive signals sent from PC.}}
         {\shortstack[l]{Incpection, observe that the arduino car moves}}
         {\shortstack[l]{}}
         {\shortstack[l]{}}
\newpage
\subsection*{T003}
\testcard{T003}{AC003}{1}{BL013}{VPQ-29}
         {\shortstack[l]{GIVEN that we have arduino car. WHEN the Qualisys measures \\
                         position. THEN the position shall be updated on PC.}}
         {\shortstack[l]{Inspection, view position feed for 6DOF in the python output}}
         {\shortstack[l]{}}
         {\shortstack[l]{}}
         
\testcard{T006}{AC006}{1}{BL011}{VPQ-12}
         {\shortstack[l]{GIVEN that we have a working simulation. WHEN we change initial  \\
                         parameters (Ex: mass). THEN the quadrotor simulation shall move\\
                         along specified path.
                }}
         {\shortstack[l]{}}
         {\shortstack[l]{}}
         {\shortstack[l]{}}
         
         
       
\subsection*{T007}
\testcard{T007}{AC007}{1}{BL012}{VPQ-21}
         {\shortstack[l]{GIVEN that we have all components. WHEN we measure mass. \\
                         THEN the quadrotor shall be less than 2.5 kg.}}
         {\shortstack[l]{}}
         {\shortstack[l]{}}
         {\shortstack[l]{}}
         
         
\subsection*{T008}
\testcard{T008}{AC008}{1}{BL012}{VPQ-21}
         {\shortstack[l]{GIVEN that we have an estimated mass AND that we have four motors.\\ 
                         WHEN we provide 50 percent thrust. THEN the quadrotor shall hover.}}
         {\shortstack[l]{See TR001}}
         {\shortstack[l]{See TR001}}
         {\shortstack[l]{}}
\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%

% Sprint 2
\testcard{TXXX}{AC010}{X}{BL014}{VPQ-59}
         {\shortstack[l]{GIVEN that we have a quadrotor, 
                    WHEN we look at markers,
                    THEN \\ 3 markers shall be mounted in the same plane and  1 marker in \\ another plane.
}}
         {\shortstack[l]{}}
         {\shortstack[l]{}}
         {\shortstack[l]{}}
         
         
\testcard{T014}{AC017}{5}{BL035 BL036}{VPQ-184 VPQ-120}
         {\shortstack[l]{GIVEN that we have a servo connected to a a variable pitch mechanism, \\ 
                         WHEN we send command for desired pitch angle in code,  THEN the \\
                         servo shall stay in this position until another command is provided }}
         {\shortstack[l]{}}
         {\shortstack[l]{TR006}}
         {\shortstack[l]{}}
         
         
%%%%%%%%%%%%%%%%%%%%%%%%%

% TR

\section{Test Reports}
\subsection{TR001}
\tr{T008}{AC008}{1}{BL012}{VPQ-21}
   {\shortstack[l]{GIVEN that we have an estimated mass AND that we have four motors.\\ 
                   WHEN we provide 50 percent thrust. THEN the quadrotor shall hover.}}
\subsubsection{\textsc{\medium Test Procedure}}

\paragraph{Test Method:}\mbox{}\\
Static Testing through analysis and calculation.

\paragraph{Test Information:}\mbox{}\\
\begin{itemize}
\item  The propeller thrust given from the supplier, is at optimal conditions so it is a theoretical value. The actual thrust differs from propeller to propeller. A variable pitch propeller is symmetric, and therefore i will have less thrust than fixed pitch propellers. The thrust given from supplier is given at FPQ. This must be considered when estimating or calculating the actual thrust from propellers.
\item Max trust in grams must be at least twice the mass of the quadrotor
\item If the quadrotor has liftoff at 50 percent trust or less, the test is fulfilled.
\item The optimal thrust of each propeller $tr_p$ is $x_1$ grams
\item This gives a total thrust of
    \begin{equation}
    \begin{split}
        tr_{tot} = x_1\cdot4 = x_2
    \end{split}
    \end{equation}
\item The total mass of the quadrotor in  grams shall be:
    \begin{equation}
    \begin{split}
        x_2 \geq 2\cdot m_{quadcopter} 
    \end{split}
    \end{equation}
\end{itemize}
\paragraph{Test Steps:}\mbox{}\\
\paragraph{Test Equipment:}\mbox{}\\
No special equipment needed.
\subsubsection{\textsc{\medium Analysis:}}
\subsubsection{\textsc{\medium Test Result(s):}}
\newpage